Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-08-27 main.tex
Explicitly state that weights and values are integers in our scheme. This will tie in nicer in the real number encoding section Removed some remaining instances of "weighted aggregation" as this has been replaced by linear-combination aggregation throughout - includes updating the paper title, and the abstract

% Title, preferably not more than 10 words.
\title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}}

@@

% Abstract of not more than 200 words.
\begin{abstract}
Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy. Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy. Existing approaches which provide such guarantees, fail to address sensor and navigator privacy in some common model-based non-linear measurement localisation methods forfeiting broad applicability. We define a cryptographically secure weighted aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation. The security requirements, leakage, and cryptographic proof are given for the private filter and weighted aggregation scheme, and simulations of the filter are used to evaluate the accuracy and performance of the method. Our approach defines a novel, computationally plausible and cryptographically private, model-based localisation filter with direct application to environments where nodes may not be fully trusted and data is considered sensitive.
\end{abstract}

@@

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_N$,
\begin{align}
    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{N^2}) &= m_1m_2\!\pmod{N}\,. \label{eqn:paillier_hom_mult}
\end{align}

@@

Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$. Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$. $n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
\begin{equation}
    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
\end{equation}
and sent to the aggregator.

@@

@@

\subsection{Integer Encoding for Real Numbers}

>>>>

% Title, preferably not more than 10 words.
\title{Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}}

@@

% Abstract of not more than 200 words.
\begin{abstract}
Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy. Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy. Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common, model-based, non-linear measurement, localisation methods and forfeit broad applicability. We define a cryptographically secure linear-combination aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation. The security requirements, leakage, and cryptographic proof are given for the private filter and aggregation scheme, and simulations of the filter are used to evaluate the accuracy and performance of the method. Our approach defines a novel, computationally plausible and cryptographically private, model-based localisation filter with direct application to environments where nodes may not be fully trusted and data is considered sensitive.
\end{abstract}

@@

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_N$,
\begin{align}
    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2) \hspace{-7pt} \pmod{N^2}) &= m_1+m_2 \hspace{-7pt} \pmod{N} \\
    \mathcal{D}(\mathcal{E}(m_1)g^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1+m_2\hspace{-7pt}\pmod{N} \\
    \mathcal{D}(\mathcal{E}(m_1)^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1m_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
\end{align}

@@

Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$. Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$. $n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
\begin{equation*}
    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
\end{equation*}
and sent to the aggregator.

@@

Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $x^{(t)}_{i,j}$ are integers, and that resulting linear combinations and summations are computed $\pmod{N}$.

@@

\subsection{Integer Encoding for Real Numbers}
Point out the integer range limit introduced by our scheme, $x<N$, for both the weights and the values.
